Stable Hot Spot Analysis (Draft)

### 2017-06-08 paper-main.tex
Create paper-main.tex

\begin{abstract}
Hotspot analysis is an essential in geo-statistics. It supports decision making by detecting points as well as areas of interest in comparison to their neighbourhood. 
But these methods are dependent on different parameters, ranging from the resolution of the study area to the size of their neighbourhood. 
This dependence can lead to instabilities of the detected hotspots, where the results can highly vary between different parameters. 
A decision maker can therefore not be sure of the validity of analysis. 
In this study, we examine the impact of key parameter on the stability of the hotspots, namely the size of the neighbourhood, the resolution and the size of the study area, as well as the influence of the ratio between those parameter.
 We compute the hotspots with the well known Getis-Ord ($G^*$) statistic as well as an modification, the \emph{Focal $G^*$} statistic. 
 The stability of the hotspot analysis is measured with the recently introduced \emph{stability of hotspots} (SoH) metric and by visual analysis. 
 We evaluate the results on real world data with the well-known yellow cab taxi data set from New York, Manhattan. 
 Our results indicate a negative impact on the stability with an increase of the size of the neighbourhood as well as a reduction of the size of the study area, regardless of the resolution.

\end{abstract}

>>>>

\begin{abstract}
Hotspot analysis is essential for geo-statistics.
It supports decision making by detecting points
as well as areas of interest in comparison to their
neighbourhood. However, these methods are dependent
on different parameters, ranging from the resolution
of the study area to the size of their neighbourhood.
This dependence can lead to instabilities of the detected
hotspots, where the results can highly vary between
different parameters. A decision maker can therefore ask
how valid the analysis actually is.
%
In this study, we examine the impact of key parameter
on the stability of the hotspots, namely the size of
the neighbourhood, the resolution and the size of the
study area, as well as the influence of the ratio between
those parameter.
%
We compute the hotspots with the well known Getis-Ord ($G^*$)
statistic as well as its modification, the \emph{Focal $G^*$} statistic.
We measure the stability of the hotspot analysis using
a recently introduced \emph{stability of hotspots} metric (SoH)
and compare the results to intuitive visual analysis.
%
We evaluate the results on real world data with the well-known
yellow cab taxi data set from New York, Manhattan.
Our results indicate a negative impact on the stability with
an increase of the size of the neighbourhood as well as
a reduction of the size of the study area, regardless of
the resolution.
\end{abstract}
